---
title: "IE_582_HW3_CelilMumcu"
output: html_document
---

```{r }
library(CRANsearcher)
library(MASS)
library(ggplot2)
library(data.table)
library(readxl)
```

## View(ConsumptionData)

```{r }
ConsumptionData <- read_excel("/Users/ASUS/Documents/GercekZamanliTuketim-01012016-29112019.xls")
##View(ConsumptionData)
```

```{r }
str(ConsumptionData)
```

## MAPE percentage error calculation, smaller MAPE means better forecast

```{r }
MAPE <- function(actual, forecast){
  maperesult= sum((abs(actual-forecast)/actual)*100)/length(actual)
  return(maperesult)
}
```

```{r }
length(ConsumptionData$Consumption)
```

```{r }
trainingdata= ConsumptionData[1:(length(ConsumptionData$Consumption)-29*24),]
testingdata= ConsumptionData[(length(ConsumptionData$Consumption)-29*24+1):34262,]
```

## there is no consumption value in the some hours of last day, to prevent the conflict i wrote 34262 manually.

```{r }
## View(testingdata)
## View(trainingdata)
MAPE48= MAPE(testingdata$Consumption,testingdata$Lag_48)
MAPE48
```

```{r }
MAPE168= MAPE(testingdata$Consumption,testingdata$Lag_168)
MAPE168
```

## in the Lag_48 and Lag_168 columns there are missing values naturally, i will omit first 168 row to make the table without NA value to prevent problems in regressions
##View(trainingdata)

```{r }
trainingdataclear= trainingdata[169:length(trainingdata$Consumption),]
##View(trainingdataclear)
```

## for the second part, i am going to try to create a linear regression by taking two requested features into account as time series analysis

```{r }
LinearRegressionModel= lm(Consumption~ Lag_48 + Lag_168, trainingdataclear)
summary(LinearRegressionModel)
```

```{r }
ForecastLinearRegressionModel= predict(LinearRegressionModel, testingdata)
MAPEpartB= MAPE(testingdata$Consumption, ForecastLinearRegressionModel)
MAPEpartB
```

## View(trainingdataclear) 33408 rows 33408/24= 1392 days
## View(testingdata) 686 rows but last 14 days doesnt make a total day, so (686-14)/24= 28 whole days + 14 hours
## for the third part, every consecutive 24 hours sum up the one day interval, (it begins at 00:00 finishes at 23:00 for training)
## i took different types of errors i dont know why, that's why i assigned hourly data via a long way as below:
## i'll train linear regression models for each hour using the same training period

```{r }
for(i in 1:1392) {
  trainingdataHourzero= trainingdataclear[1+24*(i-1),]
}
for(i in 1:1392) {
  trainingdataHourzero[i,]= trainingdataclear[1+24*(i-1),]
}
for(i in 1:1392) {
  trainingdataHour1= trainingdataclear[2+24*(i-1),]
}
for(i in 1:1392) {
  trainingdataHour1[i,]= trainingdataclear[2+24*(i-1),]
}
for(i in 1:1392) {
  trainingdataHour2= trainingdataclear[3+24*(i-1),]
}
for(i in 1:1392) {
  trainingdataHour2[i,]= trainingdataclear[3+24*(i-1),]
}
for(i in 1:1392) {
  trainingdataHour3= trainingdataclear[4+24*(i-1),]
}
for(i in 1:1392) {
  trainingdataHour3[i,]= trainingdataclear[4+24*(i-1),]
}
for(i in 1:1392) {
  trainingdataHour4= trainingdataclear[5+24*(i-1),]
}
for(i in 1:1392) {
  trainingdataHour4[i,]= trainingdataclear[5+24*(i-1),]
}
for(i in 1:1392) {
  trainingdataHour5= trainingdataclear[6+24*(i-1),]
}
for(i in 1:1392) {
  trainingdataHour5[i,]= trainingdataclear[6+24*(i-1),]
}
for(i in 1:1392) {
  trainingdataHour6= trainingdataclear[7+24*(i-1),]
}
for(i in 1:1392) {
  trainingdataHour6[i,]= trainingdataclear[7+24*(i-1),]
}
for(i in 1:1392) {
  trainingdataHour7= trainingdataclear[8+24*(i-1),]
}
for(i in 1:1392) {
  trainingdataHour7[i,]= trainingdataclear[8+24*(i-1),]
}
for(i in 1:1392) {
  trainingdataHour8= trainingdataclear[9+24*(i-1),]
}
for(i in 1:1392) {
  trainingdataHour8[i,]= trainingdataclear[9+24*(i-1),]
}
for(i in 1:1392) {
  trainingdataHour9= trainingdataclear[10+24*(i-1),]
}
for(i in 1:1392) {
  trainingdataHour9[i,]= trainingdataclear[10+24*(i-1),]
}
for(i in 1:1392) {
  trainingdataHour10= trainingdataclear[11+24*(i-1),]
}
for(i in 1:1392) {
  trainingdataHour10[i,]= trainingdataclear[11+24*(i-1),]
}
for(i in 1:1392) {
  trainingdataHour11= trainingdataclear[12+24*(i-1),]
}
for(i in 1:1392) {
  trainingdataHour11[i,]= trainingdataclear[12+24*(i-1),]
}
for(i in 1:1392) {
  trainingdataHour12= trainingdataclear[13+24*(i-1),]
}
for(i in 1:1392) {
  trainingdataHour12[i,]= trainingdataclear[13+24*(i-1),]
}
for(i in 1:1392) {
  trainingdataHour13= trainingdataclear[14+24*(i-1),]
}
for(i in 1:1392) {
  trainingdataHour13[i,]= trainingdataclear[14+24*(i-1),]
}
for(i in 1:1392) {
  trainingdataHour14= trainingdataclear[15+24*(i-1),]
}
for(i in 1:1392) {
  trainingdataHour14[i,]= trainingdataclear[15+24*(i-1),]
}
for(i in 1:1392) {
  trainingdataHour15= trainingdataclear[16+24*(i-1),]
}
for(i in 1:1392) {
  trainingdataHour15[i,]= trainingdataclear[16+24*(i-1),]
}
for(i in 1:1392) {
  trainingdataHour16= trainingdataclear[17+24*(i-1),]
}
for(i in 1:1392) {
  trainingdataHour16[i,]= trainingdataclear[17+24*(i-1),]
}
for(i in 1:1392) {
  trainingdataHour17= trainingdataclear[18+24*(i-1),]
}
for(i in 1:1392) {
  trainingdataHour17[i,]= trainingdataclear[18+24*(i-1),]
}
for(i in 1:1392) {
  trainingdataHour18= trainingdataclear[19+24*(i-1),]
}
for(i in 1:1392) {
  trainingdataHour18[i,]= trainingdataclear[19+24*(i-1),]
}
for(i in 1:1392) {
  trainingdataHour19= trainingdataclear[20+24*(i-1),]
}
for(i in 1:1392) {
  trainingdataHour19[i,]= trainingdataclear[20+24*(i-1),]
}
for(i in 1:1392) {
  trainingdataHour20= trainingdataclear[21+24*(i-1),]
}
for(i in 1:1392) {
  trainingdataHour20[i,]= trainingdataclear[21+24*(i-1),]
}
for(i in 1:1392) {
  trainingdataHour21= trainingdataclear[22+24*(i-1),]
}
for(i in 1:1392) {
  trainingdataHour21[i,]= trainingdataclear[22+24*(i-1),]
}
for(i in 1:1392) {
  trainingdataHour22= trainingdataclear[23+24*(i-1),]
}
for(i in 1:1392) {
  trainingdataHour22[i,]= trainingdataclear[23+24*(i-1),]
}
for(i in 1:1392) {
  trainingdataHour23= trainingdataclear[24+24*(i-1),]
}
for(i in 1:1392) {
  trainingdataHour23[i,]= trainingdataclear[24+24*(i-1),]
}
```

##for testing Hours

```{r }
for(i in 1:29) {
  testingdataHourzero= testingdata[1+24*(i-1),]
}
for(i in 1:29) {
  testingdataHourzero[i,]= testingdata[1+24*(i-1),]
}
for(i in 1:29) {
  testingdataHour1= testingdata[2+24*(i-1),]
}
for(i in 1:29) {
  testingdataHour1[i,]= testingdata[2+24*(i-1),]
}
for(i in 1:29) {
  testingdataHour2= testingdata[3+24*(i-1),]
}
for(i in 1:29) {
  testingdataHour2[i,]= testingdata[3+24*(i-1),]
}
for(i in 1:29) {
  testingdataHour3= testingdata[4+24*(i-1),]
}
for(i in 1:29) {
  testingdataHour3[i,]= testingdata[4+24*(i-1),]
}
for(i in 1:29) {
  testingdataHour4= testingdata[5+24*(i-1),]
}
for(i in 1:29) {
  testingdataHour4[i,]= testingdata[5+24*(i-1),]
}
for(i in 1:29) {
  testingdataHour5= testingdata[6+24*(i-1),]
}
for(i in 1:29) {
  testingdataHour5[i,]= testingdata[6+24*(i-1),]
}
for(i in 1:29) {
  testingdataHour6= testingdata[7+24*(i-1),]
}
for(i in 1:29) {
  testingdataHour6[i,]= testingdata[7+24*(i-1),]
}
for(i in 1:29) {
  testingdataHour7= testingdata[8+24*(i-1),]
}
for(i in 1:29) {
  testingdataHour7[i,]= testingdata[8+24*(i-1),]
}
for(i in 1:29) {
  testingdataHour8= testingdata[9+24*(i-1),]
}
for(i in 1:29) {
  testingdataHour8[i,]= testingdata[9+24*(i-1),]
}
for(i in 1:29) {
  testingdataHour9= testingdata[10+24*(i-1),]
}
for(i in 1:29) {
  testingdataHour9[i,]= testingdata[10+24*(i-1),]
}
for(i in 1:29) {
  testingdataHour10= testingdata[11+24*(i-1),]
}
for(i in 1:29) {
  testingdataHour10[i,]= testingdata[11+24*(i-1),]
}
for(i in 1:29) {
  testingdataHour11= testingdata[12+24*(i-1),]
}
for(i in 1:29) {
  testingdataHour11[i,]= testingdata[12+24*(i-1),]
}
for(i in 1:29) {
  testingdataHour12= testingdata[13+24*(i-1),]
}
for(i in 1:29) {
  testingdataHour12[i,]= testingdata[13+24*(i-1),]
}
for(i in 1:29) {
  testingdataHour13= testingdata[14+24*(i-1),]
}
for(i in 1:29) {
  testingdataHour13[i,]= testingdata[14+24*(i-1),]
}
for(i in 1:28) {
  testingdataHour14= testingdata[15+24*(i-1),]
}
for(i in 1:28) {
  testingdataHour14[i,]= testingdata[15+24*(i-1),]
}
for(i in 1:28) {
  testingdataHour15= testingdata[16+24*(i-1),]
}
for(i in 1:28) {
  testingdataHour15[i,]= testingdata[16+24*(i-1),]
}
for(i in 1:28) {
  testingdataHour16= testingdata[17+24*(i-1),]
}
for(i in 1:28) {
  testingdataHour16[i,]= testingdata[17+24*(i-1),]
}
for(i in 1:28) {
  testingdataHour17= testingdata[17+24*(i-1),]
}
for(i in 1:28) {
  testingdataHour17[i,]= testingdata[17+24*(i-1),]
}
for(i in 1:28) {
  testingdataHour18= testingdata[18+24*(i-1),]
}
for(i in 1:28) {
  testingdataHour18[i,]= testingdata[18+24*(i-1),]
}
for(i in 1:28) {
  testingdataHour19= testingdata[19+24*(i-1),]
}
for(i in 1:28) {
  testingdataHour19[i,]= testingdata[19+24*(i-1),]
}
for(i in 1:28) {
  testingdataHour20= testingdata[20+24*(i-1),]
}
for(i in 1:28) {
  testingdataHour20[i,]= testingdata[20+24*(i-1),]
}
for(i in 1:28) {
  testingdataHour21= testingdata[21+24*(i-1),]
}
for(i in 1:28) {
  testingdataHour21[i,]= testingdata[21+24*(i-1),]
}
for(i in 1:28) {
  testingdataHour22= testingdata[22+24*(i-1),]
}
for(i in 1:28) {
  testingdataHour22[i,]= testingdata[22+24*(i-1),]
}
for(i in 1:28) {
  testingdataHour23= testingdata[23+24*(i-1),]
}
for(i in 1:28) {
  testingdataHour23[i,]= testingdata[23+24*(i-1),]
}
```

```{r }
LinearRegressionModelHourzero= lm(Consumption~ Lag_48 + Lag_168, trainingdataHourzero)
summary(LinearRegressionModelHourzero)
```

```{r }
ForecastLinearRegressionModelHourzero= predict(LinearRegressionModelHourzero, testingdataHourzero)
MAPEHourzero= MAPE(testingdataHourzero$Consumption, ForecastLinearRegressionModelHourzero)
```

```{r }
LinearRegressionModelHour1= lm(Consumption~ Lag_48 + Lag_168, trainingdataHour1)
summary(LinearRegressionModelHour1)
ForecastLinearRegressionModelHour1= predict(LinearRegressionModelHour1, testingdataHour1)
MAPEHour1= MAPE(testingdataHour1$Consumption, ForecastLinearRegressionModelHour1)

LinearRegressionModelHour2= lm(Consumption~ Lag_48 + Lag_168, trainingdataHour2)
summary(LinearRegressionModelHour2)
ForecastLinearRegressionModelHour2= predict(LinearRegressionModelHour2, testingdataHour2)
MAPEHour2= MAPE(testingdataHour2$Consumption, ForecastLinearRegressionModelHour2)

LinearRegressionModelHour3= lm(Consumption~ Lag_48 + Lag_168, trainingdataHour3)
summary(LinearRegressionModelHour3)
ForecastLinearRegressionModelHour3= predict(LinearRegressionModelHour3, testingdataHour3)
MAPEHour3= MAPE(testingdataHour3$Consumption, ForecastLinearRegressionModelHour3)

LinearRegressionModelHour4= lm(Consumption~ Lag_48 + Lag_168, trainingdataHour4)
summary(LinearRegressionModelHour4)
ForecastLinearRegressionModelHour4= predict(LinearRegressionModelHour4, testingdataHour4)
MAPEHour4= MAPE(testingdataHour4$Consumption, ForecastLinearRegressionModelHour4)

LinearRegressionModelHour5= lm(Consumption~ Lag_48 + Lag_168, trainingdataHour5)
summary(LinearRegressionModelHour5)
ForecastLinearRegressionModelHour5= predict(LinearRegressionModelHour5, testingdataHour5)
MAPEHour5= MAPE(testingdataHour5$Consumption, ForecastLinearRegressionModelHour5)

LinearRegressionModelHour6= lm(Consumption~ Lag_48 + Lag_168, trainingdataHour6)
summary(LinearRegressionModelHour6)
ForecastLinearRegressionModelHour6= predict(LinearRegressionModelHour6, testingdataHour6)
MAPEHour6= MAPE(testingdataHour6$Consumption, ForecastLinearRegressionModelHour6)

LinearRegressionModelHour7= lm(Consumption~ Lag_48 + Lag_168, trainingdataHour7)
summary(LinearRegressionModelHour7)
ForecastLinearRegressionModelHour7= predict(LinearRegressionModelHour7, testingdataHour7)
MAPEHour7= MAPE(testingdataHour7$Consumption, ForecastLinearRegressionModelHour7)

LinearRegressionModelHour8= lm(Consumption~ Lag_48 + Lag_168, trainingdataHour8)
summary(LinearRegressionModelHour8)
ForecastLinearRegressionModelHour8= predict(LinearRegressionModelHour8, testingdataHour8)
MAPEHour8= MAPE(testingdataHour8$Consumption, ForecastLinearRegressionModelHour8)

LinearRegressionModelHour9= lm(Consumption~ Lag_48 + Lag_168, trainingdataHour9)
summary(LinearRegressionModelHour9)
ForecastLinearRegressionModelHour9= predict(LinearRegressionModelHour9, testingdataHour9)
MAPEHour9= MAPE(testingdataHour9$Consumption, ForecastLinearRegressionModelHour9)

LinearRegressionModelHour10= lm(Consumption~ Lag_48 + Lag_168, trainingdataHour10)
summary(LinearRegressionModelHour10)
ForecastLinearRegressionModelHour10= predict(LinearRegressionModelHour10, testingdataHour10)
MAPEHour10= MAPE(testingdataHour10$Consumption, ForecastLinearRegressionModelHour10)

LinearRegressionModelHour11= lm(Consumption~ Lag_48 + Lag_168, trainingdataHour11)
summary(LinearRegressionModelHour11)
ForecastLinearRegressionModelHour11= predict(LinearRegressionModelHour11, testingdataHour11)
MAPEHour11= MAPE(testingdataHour11$Consumption, ForecastLinearRegressionModelHour11)

LinearRegressionModelHour12= lm(Consumption~ Lag_48 + Lag_168, trainingdataHour12)
summary(LinearRegressionModelHour12)
ForecastLinearRegressionModelHour12= predict(LinearRegressionModelHour12, testingdataHour12)
MAPEHour12= MAPE(testingdataHour12$Consumption, ForecastLinearRegressionModelHour12)

LinearRegressionModelHour13= lm(Consumption~ Lag_48 + Lag_168, trainingdataHour13)
summary(LinearRegressionModelHour13)
ForecastLinearRegressionModelHour13= predict(LinearRegressionModelHour13, testingdataHour13)
MAPEHour13= MAPE(testingdataHour13$Consumption, ForecastLinearRegressionModelHour13)

LinearRegressionModelHour14= lm(Consumption~ Lag_48 + Lag_168, trainingdataHour14)
summary(LinearRegressionModelHour14)
ForecastLinearRegressionModelHour14= predict(LinearRegressionModelHour14, testingdataHour14)
MAPEHour14= MAPE(testingdataHour14$Consumption, ForecastLinearRegressionModelHour14)

LinearRegressionModelHour15= lm(Consumption~ Lag_48 + Lag_168, trainingdataHour15)
summary(LinearRegressionModelHour15)
ForecastLinearRegressionModelHour15= predict(LinearRegressionModelHour15, testingdataHour15)
MAPEHour15= MAPE(testingdataHour15$Consumption, ForecastLinearRegressionModelHour15)

LinearRegressionModelHour16= lm(Consumption~ Lag_48 + Lag_168, trainingdataHour16)
summary(LinearRegressionModelHour16)
ForecastLinearRegressionModelHour16= predict(LinearRegressionModelHour16, testingdataHour16)
MAPEHour16= MAPE(testingdataHour16$Consumption, ForecastLinearRegressionModelHour16)

LinearRegressionModelHour17= lm(Consumption~ Lag_48 + Lag_168, trainingdataHour17)
summary(LinearRegressionModelHour17)
ForecastLinearRegressionModelHour17= predict(LinearRegressionModelHour17, testingdataHour17)
MAPEHour17= MAPE(testingdataHour17$Consumption, ForecastLinearRegressionModelHour17)

LinearRegressionModelHour18= lm(Consumption~ Lag_48 + Lag_168, trainingdataHour18)
summary(LinearRegressionModelHour18)
ForecastLinearRegressionModelHour18= predict(LinearRegressionModelHour18, testingdataHour18)
MAPEHour18= MAPE(testingdataHour18$Consumption, ForecastLinearRegressionModelHour18)

LinearRegressionModelHour19= lm(Consumption~ Lag_48 + Lag_168, trainingdataHour19)
summary(LinearRegressionModelHour19)
ForecastLinearRegressionModelHour19= predict(LinearRegressionModelHour19, testingdataHour19)
MAPEHour19= MAPE(testingdataHour19$Consumption, ForecastLinearRegressionModelHour19)

LinearRegressionModelHour20= lm(Consumption~ Lag_48 + Lag_168, trainingdataHour20)
summary(LinearRegressionModelHour20)
ForecastLinearRegressionModelHour20= predict(LinearRegressionModelHour20, testingdataHour20)
MAPEHour20= MAPE(testingdataHour20$Consumption, ForecastLinearRegressionModelHour20)

LinearRegressionModelHour21= lm(Consumption~ Lag_48 + Lag_168, trainingdataHour21)
summary(LinearRegressionModelHour21)
ForecastLinearRegressionModelHour21= predict(LinearRegressionModelHour21, testingdataHour21)
MAPEHour21= MAPE(testingdataHour21$Consumption, ForecastLinearRegressionModelHour21)

LinearRegressionModelHour22= lm(Consumption~ Lag_48 + Lag_168, trainingdataHour22)
summary(LinearRegressionModelHour22)
ForecastLinearRegressionModelHour22= predict(LinearRegressionModelHour22, testingdataHour22)
MAPEHour22= MAPE(testingdataHour22$Consumption, ForecastLinearRegressionModelHour22)

LinearRegressionModelHour23= lm(Consumption~ Lag_48 + Lag_168, trainingdataHour23)
summary(LinearRegressionModelHour23)
ForecastLinearRegressionModelHour23= predict(LinearRegressionModelHour23, testingdataHour23)
MAPEHour23= MAPE(testingdataHour23$Consumption, ForecastLinearRegressionModelHour23)
```

```{r }
MEANofMAPESHourly= mean(MAPEHourzero,MAPEHour1,MAPEHour2,MAPEHour3,MAPEHour4,MAPEHour5,MAPEHour6,MAPEHour7,MAPEHour8,MAPEHour9,MAPEHour10,MAPEHour11,MAPEHour12,MAPEHour13,MAPEHour14,MAPEHour15,MAPEHour16,MAPEHour17,MAPEHour18,MAPEHour19,MAPEHour20,MAPEHour21,MAPEHour22,MAPEHour23)
MEANofMAPESHourly
```

## for the part f, i drew the boxplots of MAPES as follows: Smaller MAPE means smaller error in forecasting. So, LÝnearRegressionHourly gave the smallest MAPE which is 2,932 among MAPEs(it is the mean of 24 distinct hour models). When we take hourly seasonality into account, the error is decreased.

```{r }
boxplot(MAPE48,MAPE168,MAPEpartB,MEANofMAPESHourly, main= "MAPEs", names = c("Lag48","Lag168","LinReg","LRegHour"))
```
